flowCore a Bioconductor package for high throughput flow cytometry

### 2009-01-20 paper/bmc_article.tex
fix the call to featureSignif function from the feature package as some parameters have been redifined: addSignifCurv=TRUE now replaces addSignifCurvRegion=TRUE, plotFS=FALSE
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@36811 bc3139a8-67e5-0310-9ffc-ced21a209358

\author{Florian Hahne\correspondingauthor$^1$%
       \email{Florian Hahne\correspondingauthor - fhahne@fhcrc.org}%
      \and
         Nolwenn LeMeur\correspondingauthor$^{1,2}$%
         \email{Nolwenn LeMeur\correspondingauthor - nlemeur@irisa.fr}
       \and 
         Ryan R. Brinkman$^3$%
         \email{Ryan R. Brinkman - rbrinkman@bccrc.ca}%
        \and
          Byron Ellis$^4$%
          \email{Byron Ellis - byron.ellis@gmail.com}
        \and
          Perry Haaland$^5$%
          \email{Perry Haaland - Perry\_D\_Haaland@bd.com}
        \and
          Deepayan Sarkar$^1$%
          \email{Deepayan Sarkar - dsarkar@fhcrc.org}
        \and
         Josef Spidlen$^3$%
         \email{Josef Spidlen - jspidlen@bccrc.ca}
        \and
         Errol Strain$^5$%
         \email{Errol Strain - estrain@gmail.com}  
       and
          Robert Gentleman$^1$%   
          \email{Robert Gentleman - rgentlem@fhcrc.org}
        }

@@

\begin{abstract}
        % Do not use inserted blank lines (ie \\) until main body of text.
  \paragraph*{Background:} Recent advances in automation technologies
  have enabled the use of flow-cytometry high content screening
  (FH-HCS), generating large complex data sets often in clinical
  trials or drug discovery settings. However, data management and data
  analysis methods have not advanced sufficiently far from the initial
  small-scale studies to support modeling in the presence of multiple
  covariates.

  \paragraph*{Results:} We developed a set of flexible open source
  computational tools (in the R package \Rpackage{flowCore}) to
  facilitate the analysis of these complex data. A key component of
  which is having suitable data structures that support the
  application of similar operations to a collection of samples or a
  clinical cohort. In addition, our software constitutes a shared and
  extensible research platform that enables collaboration between
  bioinformaticians, computer scientists, statisticians, biologists
  and clinicians. This platform will foster the development of novel
  analytic methods for flow cytometry.

>>>>

\author{Florian Hahne\correspondingauthor$^1$%
       \email{Florian Hahne\correspondingauthor - fhahne@fhcrc.org}%
      \and
         Nolwenn LeMeur\correspondingauthor$^{1,2}$%
         \email{Nolwenn LeMeur\correspondingauthor - nlemeur@irisa.fr}
       \and 
         Ryan R. Brinkman$^3$%
         \email{Ryan R. Brinkman - rbrinkman@bccrc.ca}%
        \and
          Byron Ellis$^4$%
          \email{Byron Ellis - byron.ellis@gmail.com}
        \and
          Perry Haaland$^5$%
          \email{Perry D. Haaland - Perry\_D\_Haaland@bd.com}
        \and
          Deepayan Sarkar$^1$%
          \email{Deepayan Sarkar - dsarkar@fhcrc.org}
        \and
         Josef Spidlen$^3$%
         \email{Josef Spidlen - jspidlen@bccrc.ca}
        \and
         Errol Strain$^5$%
         \email{Errol Strain - estrain@gmail.com}  
       and
          Robert Gentleman$^1$%   
          \email{Robert Gentleman - rgentlem@fhcrc.org}
        }

@@

\begin{abstract}
        % Do not use inserted blank lines (ie \\) until main body of text.
  \paragraph*{Background:} Recent advances in automation technologies
  have enabled the use of flow cytometry high content screening
  (FH-HCS), generating large complex data sets often in clinical
  trials or drug discovery settings. However, data management and data
  analysis methods have not advanced sufficiently far from the initial
  small-scale studies to support modeling in the presence of multiple
  covariates.

  \paragraph*{Results:} We developed a set of flexible open source
  computational tools in the R package \Rpackage{flowCore} to
  facilitate the analysis of these complex data. A key component of
  which is having suitable data structures that support the
  application of similar operations to a collection of samples or a
  clinical cohort. In addition, our software constitutes a shared and
  extensible research platform that enables collaboration between
  bioinformaticians, computer scientists, statisticians, biologists
  and clinicians. This platform will foster the development of novel
  analytic methods for flow cytometry.
